Deliminative verbal reduplication in Mandarin Chinese

### 2025-06-18 replies-reviews2.tex

  \citet[50]{Ernst2014} mentions that the only possible post-verbal adverbials are participant PPs (\textit{with somebody}),
  manner or resultative V-de constructions as well as 
  duration and frequency expressions.
  (\ref{ex:VPinsert}) shows a case of inserting a frequency expression into a VP.
  This suggests that it is, in principle, possible to insert adverbials into a VP.

  \ea\label{ex:VPinsert}
    \gll \objex{kai1}  \objex{san3} \objex{ci4} \objex{men2}\\
    open three time door\\
    \glt `open the door three times'
  \z

    \item The application of MRS within the HPSG framework represents a central focus of this paper. It might be helpful to explicitly acknowledge that the integration of MRS into the HPSG framework has been explored in prior research, such as \citet{Copestakeetal2005}. Addressing this would situate the current analysis more clearly within the broader theoretical landscape and strengthen its overall credibility.

    %%%%%%%%%%%%%%%%%%%
    %%%%%%%%%%%%%%%%%%%
    \noindent
    \textbf{Answer:} We added references and particularly mentioned that MRS is also used in other
    theoretical work and in computational implementations like the Grammar Matrix and CoreGram and
    we pointed the reader to the HPSG handbook, which has a section on MRS in the chapter on
    sematnics. We also point to Müller's forthcoming textbook that contains a chapter introducing MRS.

### 2025-06-18 chapters/ch05-Analysis.tex
added more on MRS

In this section, we suggest a new lexical-rule-based analysis of aspect marking and reduplication
using Minimal Recursion Semantics (MRS; \citealt{Copestakeetal2005}). %, as proposed in \citet{LuMueller2021}.
MRS uses lists of elementary predications that are connected via pointers. Scope constraints are
represented by statements of domination. This allows for elegant ways to underspecify scope. The
details cannot be discussed here. The interested reader is referred to \citet{Copestakeetal2005}. In
what follows, we will present the elementary predications with the features assumed in MRS, but leave
out handle constraints to keep things simple.

>>>>

In this section, we suggest a new lexical-rule-based analysis of aspect marking and reduplication
using Minimal Recursion Semantics (MRS; \citealt{Copestakeetal2005}). %, as proposed in \citet{LuMueller2021}.
MRS is one instance of underspecified semantics as is currently used in theoretical and
computational work in HPSG (\citealt[Section~6]{KR2024a}, \citealt[Section~3]{BFO2002a-u},
\citealt[Section~4.4]{MuellerCoreGram}, \citealt[Chapter~5]{MuellerLehrbuch4}). The advantage of
such types of semantics is that scope relations can be left underspecified. This way it is avoided
that large numbers of analyses are assigned to single sentences. Instead sentences are paired with
underspecified semantic representations from which various readings can be derived.
MRS uses lists of elementary predications that are connected via pointers. Scope constraints are
represented by statements of domination. This allows for elegant ways to underspecify scope. The
details cannot be discussed here. The interested reader is referred to \citet{Copestakeetal2005},
\citet[Section~6]{KR2024a} or for the use of MRS in a grammar of German to \citet[Chapter~5]{MuellerLehrbuch4}. In
what follows, we will present the elementary predications with the features assumed in MRS, but leave
out handle constraints to keep things simple.
